---
title: "costly"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{costly}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(costly)
```
This development version of the costly package has been made available as part of the process of testing and documenting the package. 
Currently there are no vignettes available.

A brief overview of some of the intended use of costly tools is provided in the following articles:

- [Standardise Variable Values With Fuzzy Logic And Correspondence Tables (Country names example)](V_01.html)

- [Standardise Variable Values With Lookup Codes (Currency names example)](V_02.html)


```{r echo=FALSE, eval=FALSE}
#Not yet represented as a vignette is the logic to standardise variable values using lookup tables. The basic logic (specific to currency variables) is as follows.
Y <- CostlyCountries()
Y <- renew(Y,
           new_val_xx = add_default_currency_seed(Y@CostlySeed_r4, include_1L_chr = "Country"), 
           what_1L_chr = "seed")
Y <- renew(Y, "jw", type_1L_chr = "slot", what_1L_chr = "logic") 
Y <- renew(Y, new_val_xx = make_country_correspondences("currencies"), what_1L_chr = "correspondences") 
Y <- ratify(Y)
Z <- CostlyCurrencies()
Z <- renew(Z, new_val_xx = add_default_currency_seed(Z@CostlySeed_r4,
                                                     Ready4useDyad_r4 = Y@results_ls$Country_Output_Lookup), 
           what_1L_chr = "seed")
Z <- ratify(Z, type_1L_chr = "Lookup")
Z <- renew(Z, T, type_1L_chr = "slot", what_1L_chr = "force") 
Z <- ratify(Z, type_1L_chr = "Lookup")
```

```{r echo=FALSE}
# renew - Make "slot" default, move what to third position
# ratify - Make null default new val
```

